Nested sampling with two or more objective functions

### 2015-10-11 Paper/ms.tex
Awesome new figure
Reminder to work out expected accuracy
bits and pieces

\begin{enumerate}
\item Generate $N$ particles $\{\xx_1, ..., \xx_N\}$ from $\pi(\xx)$.
\item Calculate the {\it corner count} (Equation~\ref{eqn:corner_count})
of each particle.
\item Choose one of the particles which has corner count equal to the
minimum nonzero value.
\end{enumerate}

@@

>>>>

\begin{enumerate}
\item Generate $N$ particles $\{\xx_1, ..., \xx_N\}$ from $\pi(\xx)$.
\item Calculate the {\it corner count} (Equation~\ref{eqn:corner_count})
of each particle.
\item Choose one of the particles which has corner count equal to the
minimum nonzero value. If all particles have a corner count of zero,
the algorithm terminates. Call the selected particle particle $K$.
\item Choose one of the objective functions, and find $K$'s rank in terms
of that objective function.
\item ...
\end{enumerate}

Step 1 of the algorithm ensures that NS property 1 is trivially satisfied.

@@

\begin{figure}
\centering
\includegraphics[scale=0.5]{figures/joint.pdf}
\caption{\it The particle at the corner of the grey rectangle
has a corner count of 1, since 1 other particle is within the
grey rectangle.\label{fig:joint}}
\end{figure}

\section{What kind of accuracy can we expect?}
Imagine computing $Z(\beta_1, \beta_2)$ by looping over a grid of $\beta_2$
values and doing an NS run with respect to $L_1$ for each. For each
value of $\beta_1$ and $\beta_2$ that we're interested in, we can expect
a (marginal) ``one-sigma'' accuracy in
$\ln\left[Z(\beta_1, \beta_2)\right]$ of $\pm \sqrt{H(\beta_1, \beta_2)/N}$,
for a computational cost proportional to...
